MapReduce to My Ears\\ {\Large Using Big Data for Music Synthesis}

### 2013-05-10 writeup/paper.tex
small fixes to refs
introducing HSV more clearly

\begin{figure*}
  \centering
  \begin{minipage}[t]{.3\textwidth}
    \centering
    \includegraphics[width=.7\textwidth]{images-to-regions.png}
  \end{minipage}
  \begin{minipage}[t]{.1\textwidth}
    \raisebox{.8 in}{\Huge $\to$}
  \end{minipage}
  \begin{minipage}[t]{.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{parts-and-instruments.png}
  \end{minipage}
  \caption{Mapping a stream of three images to a nine piece musical
    score.  First each image is mapped into regions, which will be
    transformed into notes and combined into a score using a mixer.}
\end{figure*}

@@

To convert image data to musical notes, we need to establish a
bijection between the data in the image and the range of music in the
song.  The way we do this is inspired by viewing colors in images as
HSV values.  In HSV, each color has three components: a hue, a
saturation, and a value.  These components are visualized (as shown in
Figure~\ref{fig:hsv}) as a cylinder (as opposed to RGB, which views
the color space as a cube).  Each component represents:

@@

In our transformation to music, we map colors in HSV to notes in MIDI.
We do this by overlaying the circle of fifths (a circle representing
pleasing intervals called fifths in music theory) onto the circle
representing hue in HSV.  We establish the octave of the produced note
using the value of the color in HSV, and the volume of the note using
the saturation.

>>>>

\begin{figure*}
  \centering
  \begin{minipage}[t]{.3\textwidth}
    \centering
    \includegraphics[width=.7\textwidth]{images-to-regions.png}
  \end{minipage}
  \begin{minipage}[t]{.1\textwidth}
    \raisebox{.8 in}{\Huge $\to$}
  \end{minipage}
  \begin{minipage}[t]{.4\textwidth}
    \centering
    \includegraphics[width=\textwidth]{parts-and-instruments.png}
  \end{minipage}
  \caption{Mapping a stream of three images to a nine piece musical
    score.  First each image is mapped into regions, which will be
    transformed into notes and combined into a score using a mixer.}
  \label{fig:images-to-music}
\end{figure*}

@@

To convert image data to musical notes, we need to establish a
bijection between the data in the image and the range of music in the
song.  The way we do this is inspired by viewing colors in images
using a slightly unconventional color representation system: HSV.  In
HSV, each color has three components: a hue, a saturation, and a
value.  These components are visualized (as shown in
Figure~\ref{fig:hsv}) as a cylinder (as opposed to RGB, which views
the color space as a cube).  Each component represents:

@@

In our transformation to music, we map colors (natively in RGB) to HSV
and then to notes in MIDI.  We do this by overlaying the circle of
fifths (a circle representing pleasing intervals called fifths in
music theory) onto the circle representing hue in HSV.  We establish
the octave of the produced note using the value of the color in HSV,
and the volume of the note using the saturation.
